---
title: "GallupDataPreparation"
author: "Kenith"
date: '2024-02-29'
---

## 0. Subset the Gallup raw data

The version of the Gallup raw data used in this study is "Gallup_World_Poll_122023.dta". This data was released to the [UofT Map and Data Library](https://mdl.library.utoronto.ca/collections/numeric-data/gallup) on January 23, 2024.

Since the raw data file is relatively large, we used a separate environment to run the following code, which subsets the variables that we needed.

```{r eval=FALSE}
# The code in this chunk will not be run in the current Rmd
# load "dplyr"
library(dplyr)

# Import the data file "Gallup_World_Poll_122023.dta"
gallupRaw <- rio::import("Gallup_World_Poll_122023.dta")

# Capitalize some variable names to align with the orginal codebook
gallupSubset <- gallupRaw %>%
    rename(WPID = wpid, WGT = wgt, COUNTRYNEW = countrynew)

# Create a character vector of the names of the variables we're interested in
varRequired <- c(
  "WPID", "WGT", "COUNTRYNEW", "COUNTRY_ISO3",
  "YEAR_CALENDAR", "WP4", "YEAR_WAVE",
  "WP16", "WP1220"
)

# Subset gallupRaw to include only the variables specified in varRequired
gallupSubset <- gallupSubset %>% 
    select(all_of(varRequired))

# Save the gallupSubset data frame to a .rds file for later use
saveRDS(gallupSubset, "GWP_RawSubset_ageStandardizedWellbeing_240229.rds")
```

The environment used for the ABOVE code had the following specifications:
R version 4.0.3 (2020-10-10)
Release Name: Bunny-Wunnies Freak Out

Platform: x86_64-pc-linux-gnu (64-bit)

Running Under: CentOS Linux 7 (Core)

Locale: LC_CTYPE=en_CA.UTF-8;LC_NUMERIC=C;LC_TIME=en_CA.UTF-8;LC_COLLATE=en_CA.UTF-8;LC_MONETARY=en_CA.UTF-8;LC_MESSAGES=en_CA.UTF-8;LC_PAPER=en_CA.UTF-8;LC_NAME=C;LC_ADDRESS=C;LC_TELEPHONE=C;LC_MEASUREMENT=en_CA.UTF-8;LC_IDENTIFICATION=C

Base Packages: stats, graphics, grDevices, utils, datasets, methods, base

Other Packages: dplyr_1.0.6

Loaded via a namespace (and not attached): zip_2.2.0, Rcpp_1.0.6, cellranger_1.1.0, pillar_1.6.1, compiler_4.0.3, forcats_0.5.1, base64enc_0.1-3, tools_4.0.3, digest_0.6.27, uuid_0.1-4, jsonlite_1.7.2, evaluate_0.14, lifecycle_1.0.0, tibble_3.1.2, pkgconfig_2.0.3, rlang_0.4.11, openxlsx_4.2.3, rstudioapi_0.13, cli_2.5.0, IRdisplay_1.0, IRkernel_1.2, curl_4.3.1, haven_2.4.1, rio_0.5.26, repr_1.1.3, generics_0.1.0, vctrs_0.3.8, hms_1.1.0, tidyselect_1.1.1, data.table_1.14.0, R6_2.5.0, fansi_0.5.0, readxl_1.3.1, foreign_0.8-80, pbdZMQ_0.3-5, readr_1.4.0, purrr_0.3.4, magrittr_2.0.1, ellipsis_0.3.2, htmltools_0.5.1.1, utf8_1.2.1, stringi_1.6.2, crayon_1.4.1

## 1. Clean the Subset Gallup Data

### 1.1 Import the subset raw data

Once we had the subset of the Gallup data, we imported the data and loaded the necessary packages:

```{r set-up}
# Load "dplyr"
library(dplyr)

# Read the RDS file
gallupSubset <- readRDS("GWP_RawSubset_ageStandardizedWellbeing_240229.rds")
```

### 1.2 Create `YEAR_INTERVIEW` 

The existing 'YEAR_CALENDAR' and 'YEAR_WAVE' variables may not accurately represent the year a participant was interviewed. 'YEAR_CALENDAR' is based on the last interview day for all participants, while 'YEAR_WAVE' refers to the wave year. We extracted the interview year from 'WP4:Interview Date' and created a 'YEAR_INTERVIEW' variable. If the 'Interview Date' was missing, we used 'YEAR_CALENDAR' as 'YEAR_INTERVIEW'.

```{r creating-YEAR_INTERVIEW}
gallup <- gallupSubset %>%
  # Convert WP4 to a date
  mutate(WP4 = as.Date(WP4, "%m/%d/%Y")) %>%
  # Create YEAR_INTERVIEW variable
  mutate(YEAR_INTERVIEW =
           ifelse(is.na(WP4), YEAR_CALENDAR, format(WP4, format = "%Y")))
```

### 1.3 Clean 'Don't Know' and 'Refused' Responses

Gallup coded some responses as 'Don't Know' or 'Refused', which would not be meaningful for our analysis. We converted these responses to NA using the values found in the [WORLD POLL REFERENCE TOOL](https://wpr.gallup.com/).

```{r converting-responses-to-NA}
# Convert certain values to NA
gallup <- gallup %>%
  mutate(WP16 = ifelse(WP16 %in% c(98, 99), NA, WP16),
         WP1220 = ifelse(WP1220 %in% c(100), NA, WP1220))
```



The object `gallup` is now a cleaned subset of the Gallup data.

We save the Gallup cleaned data to a .rds file for later use

```{r exporting-gallup-cleaned}
saveRDS(gallup, "GWP_cleaned_ageStandardizedWellbeing_240229.rds")
```
